SPA: An Apache Spark Pilot scheduler for HPC applications

### 2019-02-26 paper.tex
some intro

\section{Introduction}
\section{Materials and Methods}\label{sec:methods}
    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}

>>>>

\section{Introduction}

In the recent years, neuroimaging Big Data has become more accessible, largely 
attributed to the growing number of open-data initiatives. However, the
processing of such large datasets using standard neuroimaging pipelines has 
become unfeasable. As a result, many researchers are moving towards Big Data 
engines, such as Apache Spark and Dask, to create their processing pipelines. 
Unlike traditional neuroimaging engines, big data engines were designed to be 
executed on commodity 
\section{Materials and Methods}\label{sec:methods}
    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}
